### 2022-05-12 supplement.Rmd

## Supplementary Methods 1 | Correlation between dependent samples

@@

## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results

>>>>

## Supplementary Methods 1: Correlation between dependent samples

@@

## Supplementary Methods 2: Bias correction and sensitivity analysis for frequentist results
